Evaluating a lightweight transcriptome assembly pipeline on two closely related ascidian species

### 2014-09-16 manuscript/main.tex
updated fixes from Titus, fig 2,4 and table 3. Added mocu trinity memory to results

The difference in assembly time and memory between diginorm and raw reads was not as large when using the Trinity assembler. Diginorm completed its assemblies several hours faster than assembling raw reads, \mytilde15 hours compared to \mytilde26 hours for \textit{M. oculata} and \mytilde24 hours compared to \mytilde39 hours for \textit{M. occulta}. \textit{M. occulta} normalized reads assembled with 23.17 GB of RAM versus 34.14 GB of RAM for the unnormalized reads (Figure~\ref{fig:time_and_memory.pdf}).

>>>>

The difference in assembly time and memory between diginorm and raw reads was not as large when using the Trinity assembler. Diginorm completed its assemblies several hours faster than assembling raw reads, \mytilde15 hours compared to \mytilde26 hours for \textit{M. oculata} and \mytilde24 hours compared to \mytilde39 hours for \textit{M. occulta}. \textit{M. oculata} unnormalized reads did not require much more memory than the normalized reads\textemdash 16.8 GB and 15.65 GB, respectively. Diginorm had a larger effect on \textit{M. occulta}, assembling \textit{M. occulta} normalized reads with 23.17 GB of RAM versus 34.14 GB of RAM for the unnormalized reads (Figure~\ref{fig:time_and_memory.pdf}).
